---
title: "MD2"
author: "Julie Norman"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Libraries
```{r}
library(readr)
library(formattable)
library(descr)
```

## Import

```{r}
df <- read_csv("export1b.csv")
agdf <- read_csv("export1ag.csv")
```

## Questions


What is the percentage of female LGBTQ+ individuals versus the percentage of male LGBTQ+ individuals?

```{r}
agdf$perc.fem.LGBTQ <- (agdf$female.LGBT..Count / agdf$LGBT..Count)*100

agdf$perc.mal.LGBTQ <- (100 - agdf$perc.fem.LGBTQ)
```

```{r}
agdf %>%
  select(c(Show, perc.fem.LGBTQ, perc.mal.LGBTQ)) %>%
  formattable()
```

The average amount of LGBTQ+ individuals in a show per season?

```{r}
mean(agdf$LGBT..Count)
```


What are the most represented identity groups in the LGBTQ+ population of the shows?

```{r}
formattable(table(df$Sexual.Orientation, df$Gender.Identity))

```


What are the most represented identity groups in the female identified LGBTQ+ population of the shows?
What are the least?

```{r}
table(df$Female.Identifying, df$Sexual.Orientation)
```



Are the LGBTQ+ characters often represented as abused and predatory?
```{r}
(table(df$Sexual.Orientation, df$Abused))


```


What is the most common character role for female LGBTQ+ characters?

```{r}
(table(df$Sexual.Orientation, df$Predatory))
```

