---
title: "MD2"
author: "Julie Norman"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Libraries
```{r}
library(readr)
#library(formattable)
library(descr)
library(dplyr)
library(formattable)
library(ggplot2)
```

## Import

```{r}
df <- read_csv("export1b.csv")
agdf <- read_csv("export1ag.csv")
```

## Questions


What is the percentage of female LGBTQ+ individuals versus the percentage of male LGBTQ+ individuals?

```{r}
agdf$perc.fem.LGBTQ <- (agdf$female.LGBT..Count / agdf$LGBT..Count)*100

agdf$perc.mal.LGBTQ <- (100 - agdf$perc.fem.LGBTQ)

# lgbt Q for entire population
```

```{r}
agdf %>%
  select(c(Show, perc.fem.LGBTQ, perc.mal.LGBTQ)) %>%
  formattable()
```

The average amount of LGBTQ+ individuals in a show per season?

```{r}
mean(agdf$LGBT..Count)

median(agdf$LGBT..Count)

mean(agdf$Count.of.characters.in.show)

```

```{r}
ggplot(agdf, aes(x = Count.of.characters.in.show, y = LGBT..Count)) +
  geom_point()
```


What are the most represented identity groups in the LGBTQ+ population of the shows?

```{r}
formattable(table(df$Sexual.Orientation, df$Gender.Identity))
```

What are the most represented identity groups in the female identified LGBTQ+ population of the shows?
What are the least?

```{r}
table(df$Female.Identifying, df$Sexual.Orientation)
```


```{r}
ggplot(df, aes(fill = Sexual.Orientation, x = Female.Identifying)) +
    geom_bar(position = "dodge")
```



Are the LGBTQ+ characters often represented as abused and predatory?
```{r}
(table(df$Sexual.Orientation, df$Abused))
```

```{r}
ggplot(df, aes(fill = Sexual.Orientation, x = Abused)) +
    geom_bar(position = "dodge")

ggplot(df, aes(x = Abused, y = ..prop.., group = 1)) +
    geom_bar()

ggplot(df, aes(x = Predatory, y = ..prop.., group = 1)) +
    geom_bar()
```


What is the most common character role for female LGBTQ+ characters?

```{r}
pred <- addmargins(table(df$Sexual.Orientation, df$Predatory), 2)
pred

role <- addmargins(table(df$Sexual.Orientation, df$Character.Role), 2)
role
```

```{r}
ggplot(df, aes(fill = Sexual.Orientation, x = Predatory)) +
    geom_bar(position = "dodge")

ggplot(df, aes(fill = Sexual.Orientation, x = Character.Role)) +
    geom_bar(position = "dodge")
```

```{r}
ggplot(df, aes(x = Sexual.Orientation)) +
  geom_bar()
```

